%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{EDUCATION}
% \cvsection{Education}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Master of Engineering, Electronic and Information Engineering} % Degree
{\href{http://www.ict.cas.cn/}{Institute of Computing Technology, Chinese Academy of Sciences} (\href{http://www.ict.cas.cn/}{ICT, CAS} \& \href{https://www.ucas.ac.cn/}{UCAS})} % Institution
{Beijing, China} % Location
{2022.09 - Exp. 2025.06} % Date(s)
{
  \begin{cvitems} % Description(s) bullet points
    \item {\textbf{GPA:} 3.79/4. \textbf{Advisor:} Prof. \href{https://scholar.google.com/citations?user=LC3SwhEAAAAJ&hl=en&oi=ao}{Yiqiang CHEN} and Prof. \href{https://scholar.google.com/citations?user=zMyg3vcAAAAJ&hl=en&oi=ao}{Xinlong JIANG}}
    \item {\textbf{Research Topic:} Asynchronous Federated Learning, Multimodal Federated Foundation Model, FL in Medical \& Healthcare.} % and Prof. \href{http://english.ict.cas.cn/people/scien/bln/202303/t20230321_328588.html}{Xinlong Jiang}}
    \item {\textbf{Main Courses:} Pattern Recognition and Machine Learning (92), Intelligent Computing System (97), Practial Optimization Algorithm and Application (94), Algorithm Design and Analysis (96), Deep Learning (92), etc.}
    \item {\textbf{Awards:} Merit Student Awards (10\%).}
    % \item {Has won the honorary title of Merit Student and the honorary title of Hainan University Volunteer Service Model.}
    % \item {Has won the first-class comprehensive scholarship in Hainan University.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Bachelor of Engineering, Software Engineering for Big data (Big data courses are taught in English)} % Degree
{\href{https://www.hainanu.edu.cn/}{School of Computer Science and Technology, Hainan University} (\href{https://en.wikipedia.org/wiki/Project_211}{211})} % Institution
{Hainan, China} % Location
{2018.09 - 2022.06} % Date(s)
{
  \begin{cvitems} % Description(s) bullet points
    \item {\textbf{GPA:} 3.68/4 (89.65/100). \textbf{Ranking:} 10/181.} %  \textit{\textbf{(Top 4\%)}}
    \item {\textbf{Main Courses:} Linear Algebra (97), Data Structure (99), Advanced Mathematics (90), C++ Programming (96), etc.}
    \item {\textbf{Awards:} The First Prize Scholarship (3\%), Outstanding Graduate Awards (3\%) and Merit Student Awards.}
  \end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
