%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Chapman Rinker} % Organization
    {9401 Jeronimo Rd, Irvine, CA 92618} % Location
    {Nov 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with Professor Soangra and developed tools for physical therapy. This work focused on providing treatment through the use of and design of embedded devices. Provides non-invasive intervention methods as an alternative means of treatment.}
        \item {Built custom board around an AVR micro-controller and flashed it with custom AVR code along with custom layout to interface with embedded components and sensors}
        \item {Designed a PCB in kicad and had the final board manufactured from a fab facility. This is a miniaturization of the original stack of boards.}
         \item {Developed QT app for data collection for Mbient sensors.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Voxx Climate Research In Association With Chapman University} % Job title
    {Voxx Analytics \& Chapman University} % Organization
    {1 University Dr, Orange, CA 92866} % Location
    { Dec 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on meta study related to analyzing climate papers from Web Of Science, and NSF.}
        \item {Built a web scraper in nightmare.js to scrape data from Web of Science (WOS), a research paper index, and also collected data from NSF grant database}
        \item {Used dplyer and R to clean and remove duplicates from WOS along with Postgres to finalized the cleaned data}
         \item {Carnegie Classification was used to rank publications from each institution along with the associated journal.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Google Code-in Mentor} % Job title
    {MovingBlocks} % Organization
    {} % Location
    { Nov 2017 - Jan 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped students learn the ins and outs of open source development and also provided support when finishing tasks. This work actively improved improved Terasology. }
        \item {Students worked on tasks that contributed work to Terasology that include: Terasology Modules, Engine, UI, User Documentation, Javadocs, research, etc ...}
        \item {Selected as mentor to visit Google campus.}
        \item {Reviewed work submitted by a student (code review, documentation review, javadocs, etc...)}
        %  \item { Helped students refine their work that actively improves Terasology}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Intern Computer Programmer} % Job title
    {LCPtracker, inc} % Organization
    {E Chapman Ave, Orange,CA 92866} % Location
    {Jun 2015 - Aug 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Implemented a mobile Xamarin application for labor compliance.}
        \item {Implemented MVVM patterns and repository patterns for an Sqlite backend}
        \item {Implemented a way to consume API request from an ASP.NET server.}
      \end{cvitems}
    }

\end{cventries}
